\clearpage
\phantomsection
\addtocontents{toc}{\vspace{-1.0em}}
\addcontentsline{toc}{section}{Библиография}

\begin{thebibliography}{99}

% --- Used citations only; labels match the dissertation numbering ---

\bibitem[1]{DIS-XY20}
Atanassov, K.
\newblock \emph{Theory of generalized nets (an algebraic aspect)}.
\newblock AMSE Review, 1984, vol.~1, no.~2, pp.~27--33.

\bibitem[2]{DIS-XY1}
Petri, C.-A.
\newblock \emph{Kommunication mit Automaten}.
\newblock PhD thesis, University of Bonn, Bonn, Germany, 1962.
\newblock (Also published as: Schriften des Instituts f{\"u}r Instrumentelle Mathematik, no.~2, Bonn, 1962.)

\bibitem[7]{DIS-Z3}
Атанасов, К.
\newblock \emph{Въведение в теорията на обобщените мрежи}.
\newblock Бургас: Понтика Принт, 1992, pp.~7--10.

\bibitem[8]{DIS-Z1}
Atanassov, K.
\newblock \emph{Generalized Nets}.
\newblock Singapore: World Scientific, 1991, pp.~9--14.

\bibitem[9]{DIS-BAM}
Atanassov, K.
\newblock \emph{On Generalized Nets Theory}.
\newblock Sofia: ``Prof. Marin Drinov'' Publishing House, 2007, pp.~11--14.

\bibitem[10]{DIS-AtanassovSotirova2017}
Атанасов, К.; Сотирова, Е.
\newblock \emph{Обобщени мрежи}.
\newblock \textnormal{София:} Академично издателство „Проф. Марин Дринов“, 2017.
\newblock 172~с.
\newblock ISBN 978-954-322-881-2.

\bibitem[11]{DIS-Orozova2011}
Орозова, Д.
\newblock \emph{Обобщеномрежови модели на интелигентни среди за обучение}.
\newblock \textnormal{София:} Академично издателство „Проф. Марин Дринов“, 2011.
\newblock 234~с.
\newblock ISBN 978-954-322-481-4.

\bibitem[12]{DIS-Georgiev1998}
Георгиев, П.~Р.
\newblock \emph{Обобщено-мрежови модели на системи базирани на знания}.
\newblock Дисертационен труд за придобиване на образователна и научна степен „доктор“,
СНС по ЕКТ, София, 1998.
\newblock Научна специалност: 02.21.05 „Системи с изкуствен интелект“.
\newblock Научен ръководител: К.~Атанасов.

\bibitem[13]{DIS-StefanovaPavlova2001}
Стефанова-Павлова, М.~М.
\newblock \emph{Моделиране на гъвкави автоматизирани производствени системи с обобщени мрежи}.
\newblock Дисертационен труд за придобиване на образователна и научна степен „доктор“,
СНС по ЕКТ, София, 2001.
\newblock Научна специалност: 01.01.12 „Информатика“.
\newblock Научен ръководител: К.~Атанасов.

\bibitem[14]{DIS-Aladjov2002}
Аладжов, Х.~Ц.
\newblock \emph{Обобщено-мрежови модели на обучение и самоорганизация и приложението им за управление на двигателна активност}.
\newblock Дисертационен труд за придобиване на образователна и научна степен „доктор“,
СНС по ЕКТ, София, 2002.
\newblock Научна специалност: 02.21.05 „Системи с изкуствен интелект“.
\newblock Научен ръководител: К.~Атанасов.

\bibitem[17]{DIS-Q148}
Starke, P.
\newblock \emph{Petri-Netze}.
\newblock Berlin: VEB Deutscher Verlag der Wissenschaften, 1980, pp.~[1--13].

\bibitem[31]{DIS-Kamada1989}
Kamada, T.; Kawai, S.
\newblock \emph{An algorithm for drawing general undirected graphs}.
\newblock Information Processing Letters, 1989, vol.~31, no.~1, pp.~7--15.

\bibitem[33]{DIS-Ellson2004}
Ellson, J.; Gansner, E.~R.; Koutsofios, E.; North, S.~C.; Woodhull, G.
\newblock \emph{Graphviz and Dynagraph -- Static and Dynamic Graph Drawing Tools}.
\newblock In: J{\"u}nger, M.; Mutzel, P. (eds.), \emph{Graph Drawing Software}, Springer, 2004, pp.~127--148.

\bibitem[39]{DIS-DimitrievTerziev}
Dimitriev, A.; Terziev, G.
\newblock \emph{Automating Creativity: Enhancing Generalized Nets with Algorithmic Drawing}.
\newblock In: \emph{Proceedings of the 22nd International Workshop on Intuitionistic Fuzzy Sets and Generalized Nets},
Warsaw, Poland, 18 Oct 2024 (in press).

\bibitem[41]{phdThesisOnlineGNRepo}
Angel Dimitriev.
\newblock \emph{phd-thesis-onlinegn}.
\newblock Angel Dimitriev's GitHub repository, 2026.
\newblock Available online: \url{https://github.com/Angeld55/phd-thesis-onlinegn} (accessed 12 Mar 2026).

\bibitem[42]{DIS-OnlineGN-video}
\newblock \emph{Увод в OnlineGN - Симулатор за обобщени мрежи}.
\newblock Video demonstration, published 12 Feb 2026.
\newblock Available online: \url{https://youtu.be/sM_Cp-pt2TU?si=kl58ruSYlCRxdJir} (accessed 12 Feb 2026).

\bibitem[43]{DIS-Nielsen1993RT}
Nielsen, J.
\newblock \emph{Response Times: The 3 Important Limits}.
\newblock Nielsen Norman Group, online article, 1993.
\newblock Available online: \url{https://www.nngroup.com/articles/response-times-3-important-limits/} (accessed 24 Dec 2025).

\bibitem[51]{DIS-RenderWebServices} Render Team.
\newblock \emph{Web Services}.
\newblock Official documentation.
\newblock Available online: \url{https://render.com/docs/web-services} (accessed 12 Feb 2026).

\bibitem[52]{MongoDBAtlasDocs} MongoDB Team.
\newblock \emph{What is MongoDB Atlas?}
\newblock Official documentation.
\newblock Available online: \url{https://www.mongodb.com/docs/atlas/} (accessed 12 Feb 2026).

\bibitem[53]{DIS-AngularDocs}
Angular Team.
\newblock \emph{What is Angular?}
\newblock Official documentation.
\newblock Available online: \url{https://angular.dev/overview} (accessed 12 Feb 2026).

\bibitem[54]{DIS-TypeScriptHandbook}
TypeScript Team.
\newblock \emph{The TypeScript Handbook}.
\newblock Official documentation.
\newblock Available online: \url{https://www.typescriptlang.org/docs/handbook/intro.html} (accessed 12 Feb 2026).

\bibitem[55]{DIS-D3Transition}
D3 Contributors.
\newblock \emph{d3-transition: Animated transitions for D3 selections}.
\newblock npm package documentation.
\newblock Available online: \url{https://www.npmjs.com/package/d3-transition} (accessed 12 Feb 2026).

\bibitem[56]{DIS-DimitrievAutomata}
Dimitriev, A.
\newblock \emph{Representing finite-state automata with generalized nets: Simulation via OnlineGN}.
\newblock Proceedings of the Jangjeon Mathematical Society, 2026, vol.~29, no.~1, pp.~156--167.
\newblock doi: 10.17777/pjms.2026.29.1.011.

\bibitem[57]{DIS-Atanassov1985GNFA}
Atanassov, K.~T.
\newblock \emph{Generalized Nets and Finite Automata}.
\newblock AMSE Review, Series ``Modelling and Simulation'', 1985, vol.~2, no.~2, pp.~1--7.

\bibitem[58]{DIS-HopcroftMotwaniUllman}
Hopcroft, J.~E.; Motwani, R.; Ullman, J.~D.
\newblock \emph{Introduction to Automata Theory, Languages, and Computation}.
\newblock 3rd ed., Addison--Wesley, 2006, pp.~[45--47].

\bibitem[59]{DIS-Kozen}
Kozen, D.~C.
\newblock \emph{Automata and Computability}.
\newblock Springer, 1997, pp.~[7--9].

\bibitem[60]{DIS-Papadimitriou}
Papadimitriou, C.~H.
\newblock \emph{Computational Complexity}.
\newblock Addison--Wesley, 1994, pp.~[13--14].

\bibitem[61]{DIS-rabin-scott}
Rabin, M.~O.; Scott, D.
\newblock \emph{Finite Automata and Their Decision Problems}.
\newblock IBM Journal of Research and Development, 1959, vol.~3, no.~2, pp.~114--125.

\bibitem[63]{DIS-wikipediaHanoi}
Wikipedia contributors.
\newblock \emph{Tower of Hanoi}.
\newblock Wikipedia, The Free Encyclopedia, 2025.
\newblock Available online: \url{https://en.wikipedia.org/w/index.php?title=Tower_of_Hanoi&oldid=1270762908} (accessed 12 Feb 2026).

\bibitem[64]{DIS-frame1945}
Frame, J.~S.
\newblock \emph{Solution of the Tower of Hanoi Problem}.
\newblock American Mathematical Monthly, 1945, vol.~52, no.~10, pp.~596--604.

\bibitem[65]{CLRS_TowerOfHanoi}
Cormen, T.~H.; Leiserson, C.~E.; Rivest, R.~L.; Stein, C.
\newblock \emph{Introduction to Algorithms}.
\newblock 3rd ed., Cambridge, MA, USA: MIT Press, 2009, pp.~[4--10].

\bibitem[78]{DIS-Stratiev2023_1}
Stratiev, D.~D.; Dimitriev, A.; Stratiev, D.; Atanassov, K.
\newblock \emph{Modeling the Production Process of Fuel Gas, LPG, Propylene, and Polypropylene in a Petroleum Refinery Using Generalized Nets}.
\newblock Mathematics, 2023, vol.~11, art.~3800.

\bibitem[79]{DIS-Zhou2017}
Zhou, J.; Reniers, G.; Zhang, L.
\newblock \emph{A weighted fuzzy Petri-net based approach for security risk assessment in the chemical industry}.
\newblock Chemical Engineering Science, 2017, vol.~174, pp.~136--145.

\bibitem[80]{Infosys2018}
Infosys Limited.
\newblock \emph{Predictive Analytics and Dynamic Optimization: The Sweet Spot in Refinery Planning}.
\newblock White paper, 2018.
\newblock Available online: \url{https://www.infosys.com/industries/oil-and-gas/insights/documents/sweet-spot-refinery-planning.pdf} (accessed 14 Dec 2022).

\bibitem[81]{40}
Zhang, L.; Yuan, Z.; Chen, B.
\newblock \emph{Refinery-wide planning operations under uncertainty via robust optimization approach coupled with global optimization}.
\newblock Computers \& Chemical Engineering, 2021, vol.~146, art.~107205.
\newblock doi: 10.1016/j.compchemeng.2020.107205.

\bibitem[82]{DIS-87}
Stratiev, D.~D.; Zoteva, D.; Stratiev, D.~S.; Atanassov, K.
\newblock \emph{Modelling the Process of Production of Automotive Gasoline by the Use of Generalized Nets}.
\newblock In: \emph{Uncertainty and Imprecision in Decision Making and Decision Support: New Advances, Challenges, and Perspectives},
Lecture Notes in Networks and Systems, vol.~338, Springer, 2022, pp.~349--365.
\newblock doi: 10.1007/978-3-030-95929-6\_27.

\bibitem[83]{DIS-88}
Stratiev, D.~D.; Stratiev, D.; Atanassov, K.
\newblock \emph{Modelling the Process of Production of Diesel Fuels by the Use of Generalized Nets}.
\newblock Mathematics, 2021, vol.~9, art.~2351.
\newblock doi: 10.3390/math9192351.

\bibitem[89]{DIS-Stratiev2023_2}
Stratiev, D.~D.; Dimitriev, A.; Stratiev, D.; Atanassov, K.
\newblock \emph{Generalized Net Model of Heavy Oil Products' Manufacturing in Petroleum Refinery}.
\newblock Mathematics, 2023, vol.~11, art.~4753.

\bibitem[91]{DIS-96}
Kaiser, M.~J.; De Klerk, A.; Gary, J.~H.; Handwerk, G.~E.
\newblock \emph{Petroleum Refining: Technology, Economics, and Markets}.
\newblock 6th ed., Boca Raton, FL, USA: CRC Press, 2020, pp.~1--722.

\bibitem[92]{DIS-97}
Merdrignac, I.; Espinat, D.
\newblock \emph{Physicochemical characterization of petroleum fractions: The state of the art}.
\newblock Oil \& Gas Science and Technology -- Rev. IFP, 2007, vol.~62, pp.~8--29.

\bibitem[94]{DIS-103}
Gaikwad, R.~W.; Warade, A.~R.; Bhagat, S.~L.; Bhasarkar, J.~B.
\newblock \emph{Optimization and simulation of refinery vacuum column with an overhead condenser}.
\newblock Materials Today: Proceedings, 2022, vol.~57, pp.~1593--1597.
\newblock doi: 10.1016/j.matpr.2021.12.175.

\end{thebibliography}